---
title: TradeMe API
author: Nathan Moore
date: '2024-07-29'
slug: []
categories: []
tags: []
image: ''
showonlyimage: no
draft: true
---

Using the TradeMe API to get open home times. 

<!--more-->

https://www.leonstirkwang.com/


```{r}

library(tidyverse)
library(httr)
library(jsonlite)

url <- 'https://api.tmsandbox.co.nz/v1/Search/Property/Residential.json'

oauth_consumer_key <- 'D53AB0CB5EC5D682029496F60B5D7393'
oauth_token <- 'F83758900E3AB621C4276161FD9BF18E'
oauth_signature_method <- 'PLAINTEXT'
oauth_signature <- '498F193869048CC84B0730C85BB62E1B%266341658CF69EE809862AF78B1071C675'

header <- paste('OAuth oauth_consumer_key=', oauth_consumer_key,
                   ',oauth_token=', oauth_token,
                   ',oauth_signature_method=', oauth_signature_method,
                   ',oauth_signature=', oauth_signature,
                   sep = '')

result <- GET(url, add_headers(Authorization = header))
```

```{r}
result
```

Yay! 

```{r}
dat <- fromJSON(content(result, as='text'))
dat$List %>% as_tibble()
dat_tibble <- dat$List %>% as_tibble()
```

```{r}
dat$TotalCount

```

Let us also steal the loop code from Leon

```{r message=FALSE}
## Request loop
rows <- 500
stop <- 0
i <- 1
dat <- list()
while(stop < 1) {
  url_page <- paste0(url,'?rows=',rows,'&page=',i)
  tmp <- GET(url_page, add_headers(Authorization = header))
  dat[[i]] <- tmp
  stop <- if(ceiling(fromJSON(content(tmp, as='text'))$TotalCount/rows) == i){1}else{0}
  i <- i+1
}
rm(i, stop, rows, url_page)

## Melt paginated data together
df <- bind_rows(lapply(dat, function(x) {
  fromJSON(content(x, as='text'))$List %>% as.data.frame() }
))
```

And then some time conversion

```{r}
## Date variable conversion
convDate <- function(x) {
  as.Date((x %>% str_remove_all('[/Date()]') %>% as.numeric())/1000/60/60/24, origin = "1970-01-01")
}

df$StartDate <- convDate(df$StartDate)
df$EndDate   <- convDate(df$EndDate)
df$AsAt <- convDate(df$AsAt)

```

Plus pricing

```{r}
## Price variables
df$price_integer <- df$PriceDisplay %>% str_extract_all('\\d') %>%
  lapply(., function(x) { paste(x, collapse = '') }) %>% unlist %>% as.integer()

df$price_category <- df$PriceDisplay %>% str_extract_all('[^\\d:,$]') %>%
  lapply(., function(x) { paste(x, collapse = '') }) %>% unlist %>% str_remove(' $') %>% as.factor
```

Plus maybe a map

```{r}
library(sf)
library(tmap)

df$lon <- df$GeographicLocation$Longitude
df$lat <- df$GeographicLocation$Latitude

df <- df |> 
  filter(lat <= -30 & 
        lat >= -50 & 
        lon >= 165 & 
        lon <= 180)

df_sf <- st_as_sf(x = df, coords = c('lon', 'lat'), crs = 4326)

## Visualise
tmap_mode('view')
## the code as it was on the page
# tm_shape(df_sf %>% select(geometry) + tm_dots()

## my best guess as to the proper code
df_sf %>% select(geometry) |> tm_shape() + tm_dots()


```

Error in st_as_sf.data.frame(x = df, coords = c("lon", "lat"), crs = 4326) : 
  missing values in coordinates not allowed
  
I don't think there are missing values, but there are some weird ones. We can have a look at the df and set some reasonable values. 

This is no good: -15.96110 -178.079880, and neither is this: 51.64397 -121.295010

Latitude between -30 and -50, Longitude between 165 and 180. 

The code has been changed above. 

What I'm really interested in is the OpenHomes column. 
  
```{r}
df$OpenHomes |> head()
```
  
These are all blank dataframes, how do I filter them? 

This row is not blank, but it's very hardcoded. 

```{r}

df[15,]

```

This one
https://stackoverflow.com/questions/71039911/drop-all-rows-in-a-dataframe-that-have-an-empty-list-in-a-specified-column-in-r#comment125583803_71039911 

```{r}
df[lengths(df$OpenHomes) > 0, ]
```


