---
title: Image Resize
author: Nathan Moore
date: '2025-08-13'
slug: blog-image-resize
categories:
  - Code
tags: []
draft: yes
image: ''
showonlyimage: no
---

Decrease the size of the images in this repository / on this blog.

<!--more-->

Most of my images have been resized one way or another, but some of them are still too big. Many of them because I saved them from Facebook where the original posts lived. I only need them to be as large as they will be displayed on the screen for this site. What's a good size? 1000px wide? 100KB? What's the relationship between these measures?

This is my script to go through this blog's folders and resize images down to an acceptable size. Should I do this for python and R? Yes!

First, we should collect some metrics about the sizes and dimensions of of what we already have.

The folder location for all the images is here:

`C:\Users\NathanMoore\code\creative-website\static\img`

```{r}
library(here)

here::here()

```

```{python}
import os

os.getcwd()

```

Interesting that the R code is for the repository, and the python code is for the current file. Can we find a way to get git directory for python?

<https://stackoverflow.com/questions/22081209/find-the-root-of-the-git-repository-where-the-file-lives>

<https://github.com/gitpython-developers/GitPython>\
<https://gitpython.readthedocs.io/en/stable/>

This is great but I really only need the one function and method.

```{python}
import git

repo = git.Repo('.', search_parent_directories=True)
repo.working_tree_dir
```

Nice.

It looks like I can keep switching between R and python environments so I'm going to develop these two techniques at the same time rather than one after the other.

```{r}
r_fldr = here::here()

r_fldr = paste0(r_fldr, '/static/img/')

r_fldr
```

```{python}

py_fldr = repo.working_tree_dir + '\\static\\img\\'

print(py_fldr)
```

I want to use `os.walk()` for python but I'm not sure what the equivalent is in R. It looks like `list.files()` is the way to go.


```{r}
r_files = list.files(r_fldr, full.names = TRUE, recursive = TRUE)
head(r_files)
```

Always love a list comprehension. 

<https://stackoverflow.com/questions/3207219/how-do-i-list-all-files-of-a-directory#comment128971338_3207973>

```{python}

py_files = [os.path.join(dirpath,f) for (dirpath, dirnames, filenames) in os.walk(py_fldr) for f in filenames] 
py_files[:5]
```

The same results for each of these operations: 292 files.

we can now get files sizes and image widths

```{r}
r_sizes = lapply(r_files, file.size)
head(r_sizes)
```

```{python}
py_sizes = [os.stat(f).st_size for f in py_files]
py_sizes[:5]
```

This is fine so far, but I'm going to have more vectors and lists, and this is better contained in a dataframe. 

```{r}
library(tidyverse)

r_df = tibble(r_files) |> 
       rename(filename = r_files)

r_df = r_df |> 
       mutate(filesize = file.size(filename))

```

Good! I always feel weird importing all of tidyverse but I have a hard time remembering which library contains which functions after a few years not using R. 

```{python}
import pandas as pd

py_df = pd.DataFrame(py_files, columns=['filename'])

py_df['filesize'] = py_df['filename'].map(lambda x: os.stat(x).st_size)

```

Also, dimensions. 

I struggled with this for a while, with the interaction between mutate, if_else, read.bitmap. 
I think I need to create a function which I can then simply use with mutate. 
Kind of simply, because I actually want the height and width of the image, so `map` for the `list` function output, and then `unnest`. 

```{r warning=FALSE}

library(readbitmap)

# this was the closest I got but doesn't seem to work. 
# I think if_else evaluates the thing even though the condition is false? 
# and read.bitmap cannot handle a mp4 file
# r_df = r_df |> 
#        rowwise() |>
#        mutate(dims = if_else(str_detect(filename, '.jpg'),                              
#                              read.bitmap(filename),
#                              99))


height_width <- function(filenames) {
  h = array(dim = length(filenames))
  w = array(dim = length(filenames))
  for (i in seq_along(filenames)) {
    k = filenames[i]
    if (str_detect(k, '.png') || str_detect(k, '.jpg')) {
      img = read.bitmap(k)
      h[i] = dim(img)[1]
      w[i] = dim(img)[2]
    } else {
      h[i] = 0
      w[i] = 0
    }
  }
  list(height = h, width = w)
}

r_df = r_df |> 
       mutate(dims = map(filename, height_width)) |> 
       unnest_wider(dims) |> 
       mutate(filetype = tools::file_ext(filename))

table(r_df$filetype)

```

Now, for python. I think I'll jump to the same approach with a lambda for pandas. 
Not quite a lambda, but I went through `apply()` and then found this application of `zip()`

https://stackoverflow.com/questions/16236684/apply-pandas-function-to-column-to-create-multiple-new-columns


```{python}

from PIL import Image

def height_width(filename): 
    # filename = row['filename']
    if '.jpg' in filename or '.png' in filename:
        with Image.open(filename) as img: 
            width, height = img.size
    else: 
        width, height = 0, 0
    return width, height
        
# py_df['width'], py_df['height'] = py_df['filename'].map(lambda x: height_width(x))

# py_df[['width','height']] = py_df.apply(height_width, axis='columns')

py_df['width'], py_df['height'] = zip(*py_df['filename'].map(height_width))

py_df['filetype'] = py_df['filename'].map(lambda x: x.split('.')[-1])

py_df['filetype'].value_counts()

```

Now, to make a chart out of the dataframes. I think a couple of histograms each, one for filesize, one for width, and a scatter plot that compares two. The images are not all in one orientation, portrait/landscape, so maybe I should take the maximum out of width and height? 

```{r}

r_df = r_df |> 
    rowwise() |> 
    mutate(max_dim = max(width, height))

```

```{r}

r_df |> 
    filter(width != 0) |> 
    ggplot(aes(filesize)) + 
    geom_histogram()

r_df |> 
    filter(width != 0) |> 
    ggplot(aes(max_dim)) + 
    geom_histogram()

r_df |> 
    filter(width != 0) |> 
    ggplot(aes(max_dim, filesize)) + 
    geom_point()

```

Python charts, which requires a search, because I always have to look something up. w3schools is the first result, which will give me what I need. https://www.w3schools.com/python/matplotlib_histograms.asp 

```{python}

import matplotlib.pyplot as plt

py_df_img = py_df[py_df['width'] != 0]

py_df_img['max_dim'] = py_df_img[['width', 'height']].max(axis=1)

plt.hist(py_df_img['filesize'], bins=30)

plt.show()

plt.close()

```

```{python}

plt.hist(py_df_img['max_dim'], bins=30)
plt.show()

plt.close()

```

```{python}

plt.scatter(py_df_img['max_dim'], py_df_img['filesize'])
plt.show()

plt.close()

```

Nice! We have some plots. I don't want to do too much with the charts. 

Now we need to change the size of the images. I'll take a backup, of course. Before the changes, the `img` folder size on disk is 40.6MB. 

ChatGPT to write some code? I'll give it a go. 

```{python eval=FALSE}
import os
from PIL import Image

def shrink_images(input_folder, output_folder, max_size=(800, 800), quality=70):
    """
    Shrink all images in a folder (including subfolders) and save them to output_folder.
    
    Args:
        input_folder (str): Path to input images.
        output_folder (str): Path to save reduced images.
        max_size (tuple): Max width, height (keeps aspect ratio).
        quality (int): JPEG quality (1-100).
    """
    # Collect all image paths
    image_files = []
    for root, _, files in os.walk(input_folder):
        for filename in files:
            if filename.lower().endswith((".jpg", ".png")):
                image_files.append(os.path.join(root, filename))

    total = len(image_files)
    print(f"Found {total} images to process.")

    # Process images with counter
    for i, input_path in enumerate(image_files, start=1):
        relative_path = os.path.relpath(os.path.dirname(input_path), input_folder)
        output_dir = os.path.join(output_folder, relative_path)
        os.makedirs(output_dir, exist_ok=True)

        output_path = os.path.join(output_dir, os.path.basename(input_path))

        with Image.open(input_path) as img:
            img.thumbnail(max_size)

            if img.mode in ("RGBA", "P"):
                img = img.convert("RGB")

            img.save(output_path, optimize=True, quality=quality)

        print(f"[{i}/{total}] Saved: {output_path}")

# Example usage
shrink_images("input_images", "output_images", max_size=(800, 800), quality=70)

```

This isn't quite right because I'm not calling this as a script operating on the files themselves. Maybe I should? I can take most of this and loop through the dataframe (even though that's not ideal as a programming paradigm). 

First thing is not having to save the folder manually - replace 'img' in the path to save to a different location. 

```{python}
os.makedirs('C:\\Users\\NathanMoore\\code\\creative-website\\static\\output\\')
```


```{python}
from PIL import Image

max_size = (1000,1000)

for f,type in zip(py_df['filename'],py_df['filetype']):
    if type in ('jpg','png'):
        out = f.replace('img', 'output')
        os.makedirs(os.path.dirname(out), exist_ok=True)
      
        with Image.open(f) as img: 
            img.thumbnail(max_size)
            img.save(out)

```

